---
title: "P8105 HW 1"
author: "hwp2110 / Helen Peng"
output: github_document
---

# Problem 1

```{r message=FALSE, warning=FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")

# names(penguins)
```

The variables in this dataset are `species`, `island`, `bill_length_mm`, `bill_depth_mm`, `flipper_length_mm`, `body_mass_g`, `sex`, and `year`. The dataset has `r ncol(penguins)` columns and `r nrow(penguins)` rows. The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm. 

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("scatterplot.png")
```
# Problem 2

```{r}
problem_df = tibble(
  num_var = rnorm(10),
  log_var = num_var > 0,
  char_var = c("a","b","c","d","e","f","g","h","i","j"),
  fact_var = factor(sample(c("low","middle","high"), size = 10, replace = TRUE))
)

problem_df
```

```{r eval = FALSE}
mean(pull(problem_df, num_var), na.rm = TRUE)
mean(pull(problem_df, log_var), na.rm = TRUE)
mean(pull(problem_df, char_var), na.rm = TRUE)
mean(pull(problem_df, fact_var), na.rm = TRUE)

as.numeric(mean(pull(problem_df, log_var), na.rm = TRUE))
as.numeric(mean(pull(problem_df, char_var), na.rm = TRUE))
as.numeric(mean(pull(problem_df, fact_var), na.rm = TRUE))
```
Taking the mean of a numeric vector or a logical vector work but not taking the mean of a character vector or a factor vector. Even after using the function `as.numeric` only logical and numeric vectors work. You would get warning that says argument is not numeric or logical: returning NA (not applicable).


